Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2017-03-14 code/rmarkdown/article.Rmd
move pvalString delcaration to initialization

```{r,include=FALSE}
# load .rda file
checkpoint::checkpoint('2016-11-26', R.version='3.3.2', scanForPackages=FALSE)
try(session::restore.session('data/final/results.rda'))
pvalString <- lazyWeave::pvalString

>>>>

```{r,include=FALSE}
# load .rda file
checkpoint::checkpoint('2016-11-26', R.version='3.3.2', scanForPackages=FALSE)
try(session::restore.session('data/final/results.rda'))
